Quantifying unmet ICU beds in tertiary hospitals in urban India using Propensity

### 2022-09-21 manuscript.Rmd
21 kväll

---
title: 'Quantifying unmet ICU beds in tertiary hospitals in urban India using Prospective
  Score Matching '
author: "Maria Eriksson"
output:
  word_document: default
  html_document: default
bibliography: bibliography.bib
csl: vancouver.csl
---

@@

Background
----------
Trauma/Injury is a substantial global health problem that disproportionately affects low and middle-income countries (LMIC), resulting in significant mortality and morbidity @traumaLMIC. The annual mortality from injury in India amount to one million casualties @onemilliondead. Half of trauma mortality in India occur in-hospital, and in-hospital trauma mortality in Indian hospitals was double that of high-income countries @indiantrauma. Health care professionals in many LMIC testify that their medical assessment oftentimes is that a trauma patient should be admitted to the ICU, but aren’t because such resources are scarce, overloaded and unavailable. Their medical judgement is that the lives of these patients were salvageable, and that these patients died as a direct result of not being admitted to the ICU @stuffLMICdoctorssay. Globally, an estimated two million lives could be saved annually, if the appropriate and timely trauma care provided by hospitals in many high-income countries were available and provided in low to-middle-income countries (LMICs) @livessaved

@@

The TITCO-I data set is analyzed mathemathically in pursuit of suitable predictor variables. The data set is divided into two subgroups, the cohort that were admitted to the ICU and the cohort that wasn't. In comparison between these subgroups, identify variables that distinguishes the former from the latter.

@@

For many parameters the difference is small, perhaps because of a crowd out effect. For instance, the total Glascow coma scale score is high and quite similar for the non-ICU subset versus the ICU subset, the difference between the average of the groups is 2 points. However, considered individually, low scores in either category is a high propensity to admit a patient to the ICU, as demonstrated in the comparison of quantitative parameters.

>>>>

---
title: 'Quantifying unmet ICU beds in tertiary hospitals in urban India using Propensity
  Score Matching '
author: "Maria Eriksson"
output:
  html_document: default
  word_document: default
bibliography: bibliography.bib
csl: vancouver.csl
---

@@

Background
----------
Trauma/Injury is a substantial global health problem that disproportionately affects low and middle-income countries (LMIC), resulting in significant mortality and morbidity @traumaLMIC. Despite having only 1% of the global vehicle fleet, a disproportionate 10% of global traffic casualties occur in India @indiantrauma. The annual mortality from injury in India amount to one million casualties @onemilliondead. Half of trauma mortality in India occur in-hospital, and in-hospital trauma mortality in Indian hospitals was double that of high-income countries @indiantrauma.

Health care professionals in many LMIC testify that their medical assessment oftentimes is that a trauma patient should be admitted to the ICU, but aren’t because such resources are scarce, overloaded and unavailable. Their medical judgement is that the lives of these patients were salvageable, and that these patients died as a direct result of not being admitted to the ICU @stuffLMICdoctorssay. Globally, an estimated two million lives could be saved annually, if the appropriate and timely trauma care provided by hospitals in many high-income countries were available and provided in low to-middle-income countries (LMICs) @livessaved

@@

The TITCO-I data set is analyzed mathemathically in pursuit of suitable predictor variables. The data set is divided into two subgroups, the cohort that were admitted to the ICU and the cohort that wasn't. In comparison between these subgroups, identify variables that distinguishes the former from the latter. The quantitative and qualitative properties were considered separately.

@@

For many parameters the difference is small, perhaps because of a crowd out effect. For instance, the total Glascow coma scale score is high and quite similar for the non-ICU subset versus the ICU subset, the difference between the average of the groups is 2 points. However, low scores in either category is a high propensity to admit a patient to the ICU, as demonstrated in the comparison of quantitative parameters.
